Stack Safety as a Security Property

### 2020-07-01 main.tex
Started on observational conf section

\leo{PUT is completely ambiguous as a choice of abbreviation. Just ``Pre''
  seems better}
The {\it prefUpTo} operation \(\PUT(\Trace,f)\) takes a trace \(T\)
and a predicate on elements \(f\) and gives the prefix of \(T\)
ending with the first element on which \(f\) holds, coinductively:

@@

\sna{Version for stepping from a state}
\definition{Confidential Execution}

  Stack confidentiality, below, is a property of a system that, from a call to
  a return, each trace obeys a local confidentiality property,
  {\it confidential execution}.

  We will say that a state \(\mpstate{\mach}{\pol}\) satisfies confidential
  execution with regard to a contour \(\contour\) and an ending condition
  \(R\) that is a predicate on machine states if, for all variant states
  \(\mach' \approx_\contour \mach\), the induced traces from \(\mach\) and
  \(\mach'\) behave the same across three cases. Let
  \(\mpstate{\mach}{\pol} \hookrightarrow \MPT | R\) and
  \(\mach' \hookrightarrow \machT | R\).

  If \(\MPT\) ends with a state \(\mach_r\) and \(R\ \mach_r\), then \(\machT\)
  ends with a state \(\mach_r'\) such that \(R\ \mach_r'\). \(\MPT\) and
  \(\machT\) are observationally equivalent, and for each component
  \(\component\) such that \(\contour(\component) = \HIGHSEC\),
  \(\mach_r(\component) = \mach_r'(\component)\).

  If \(\MPT\) is infinite, then \(\machT\) is infinite, and they are
  observationally equivalent.

  If \(\MPT\) ends before \(R\) ever holds, meaning that it halted due to a
  policy violation, then it is a strict observational prefix of \(\machT\),
  which must be infinite.

@@

    \definition{Observable Confidentiality}

      Observable confidentiality is concerned with whether high confidentiality
      data influences observable both behavior during and after a call. As with
      eager confidentiality, we will compare the behavior of the trace induced
      by a state to another induced by its variant. But if the original returns,
      before continuing, we must reset the variant to conform with the original
      state.

@@

      A system enjoys observable confidentiality with respect to \(\callmap\)
      and \(\codemap\) if for any initial state \(\mach_0\), each adjacent pair
      of a call state \(\mach_c\) and a state \(\mach_e\) with policy state
      \(\pol_e\) in the inducted trace from
      \(\mpstate{\mach_0}{\mathit{pinit}(\mach_0)}\), and each variant
      \(\mach_e' \approx_\contour \mach_e'\) where
      \(\contour = \mathit{Cof}(\mach_c, \funid, n)\), one of two cases holds
      on the induced traces from \(\mach_e\) and \(\mach_e'\).

      If \(\mpstate{\mach_e}{\pol_e} \hookrightarrow_P \MPT_1 | \ret{\mach_c}\)
      with \(\MPT_1\) the trace within the callee ending with the machine state
      \(\mach_r\), the first state to return to the caller, and policy state
      \(\pol_r\), then the there is a return state \(\mach_r'\) reached by the
      trace from the variant, \(\mach_c' \hookrightarrow \machT_1 |
      \ret{\mach_c}\). Let \(\mach_r'' = \mathit{restore}(\contour,\mach_e,
      \mach_e',\mach_r,\mach_r')\), and let the induced traces from the
      returned states be \(\mpstate{\mach_r}{\pol_r} \hookrightarrow_P \MPT_2\)
      and \(\mach_r'' \hookrightarrow \machT_2\). With the callee and caller
      traces joined, the traces are observationally equivalent up to policy
      failures: \(\MPT_1 \cdot \MPT_2 \sim_P \machT_1 \cdot \machT_2\).

      The case in which the induced trace does not return is the same as in the
      eager property: the variant trace also does not return, and the induced
      traces are observationally equivalent up to policy failure.

>>>>

% SNA: fixed
%\leo{PUT is completely ambiguous as a choice of abbreviation. Just ``Pre''
%  seems better}
The {\it prefUpTo} operation \(\PUT(\Trace,f)\) takes a trace \(T\)
and a predicate on elements \(f\) and gives the prefix of \(T\)
ending with the first element on which \(f\) holds, coinductively:

@@

@@

    \definition{Observable Trace Confidentiality}

      Trace confidentiality is a property of two traces whose initial machine
      states are variations, with two sub-properties. First, the behavioral
      condition -- that their observable behaviors prior to the end of the
      trace are equivalent -- reflects the intuition that secret values should
      not influence visible behavior. Second, we have the end condition that
      their final states (if any) are equal up to the original variation. The
      end condition over-approximates the extension of the behavioral condition
      to future execution.

      We introduce {\em observable trace confidentiality}, which extends the
      behavioral condition to apply to execution from the final state on.
      This requires restoring varied components to their original values,
      since after return they will once again be accessible legitimately.

      [Example goes here, showing how, when we return from a call, execution
      becomes incoherent unless the state is restored.]

@@

      A pair of traces \(\MPT\) and \(\machT\) starting from \(\mach_c\) and
      \(\mach_c'\), respectively, with \(\mach_c \approx_\contour \mach_c'\),
      enjoy observable trace confidentiality with respect to \(\contour\) if
      two conditions hold:

      The two traces are observationally equivalent: \(\pi_o(\MPT) \eqsim_O
      \pi_o(\machT)\).

      If \(\MPT\) is finite and ends with the state
      \(\mpostate{\mach_r}{\pol_r}{\obs_r}\), then \(\machT\) is finite. Let
      \(\mach_r'\) be the final state of \(\machT\). Then the induced traces
      \(\mpstate{\mach_r}{\pol_r} \hookrightarrow \MPT'\) and
      \(\mathit{restore}(\contour,\mach_c,\mach_c',\mach_r,\mach_r')
      \hookrightarrow \machT'\) are observationally prefixed,
      \(\pi_o(\MPT') \lesssim_O \pi_o(\machT')\).

      \sna{Structured like this, we need to start with the call state, not
           the entry. That's because we need to know what to restore to.
           But we could also define restore in the stack confidentiality
           section, maybe?}

    \definition{Observable Stack Confidentiality}
